---
title: "TidyTemplate"
date: 2021-03-02
output: html_output
---

# TidyTuesday


```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(tidytuesdayR)
library(ggplot2)
library(patchwork)
```

# Load the weekly Data

Download the weekly data and make available in the `tt` object.

```{r Load}

tt <- tt_load("2019-06-04")

```

# Glimpse Data

Take an initial look at the format of the data available.

```{r Glimpse}

tt %>% 
  map(glimpse)

```

# Wrangle

Explore the data and process it into a nice format for plotting! Access each dataset by name by using a dollarsign after the `tt` object and then the name of the data set.

```{r Wrangle}
data <- tt$ramen_ratings

data <- within(data, style[is.na(data$style)] <- 'Pack')

asiatic_countries <- c("Thailand", "Japan","Taiwan","South Korea","Hong Kong","Malaysia","China","Philippines","Vietnam","Bangladesh","Singapore","Indonesia","India","Phlippines","Nepal","Myanmar")

data <- data %>%
  select(- c(brand, variety, review_number)) %>%
  filter(country %in% asiatic_countries) %>%
  group_by(country, style) %>%
  summarise(n=n())%>%
  ungroup() %>% 
  complete(country, nesting(style), fill = list(n = 0))


```


# Visualize

Using your processed dataset, create your unique visualization.

```{r Visualize}

generate_donuts <- function(data = data){
  countries <- unique(data$country)
  plist <- list()
  for (i in seq_along(countries)){
    df <- data %>%
          filter(country == countries[i])
    df$fraction = df$n / sum(df$n)
    df$ymax = cumsum(df$fraction)
    df$ymin = c(0, head(df$ymax, n=-1))
    df$labelPosition <- (df$ymax + df$ymin) / 2
    df$label <- paste0(df$style, "\n value: ", df$n)
  
    p <- ggplot(df, aes(ymax=ymax, ymin=ymin, xmax=4, xmin=3, fill=style)) +
          geom_rect() +
          coord_polar(theta="y") + 
          ggtitle(countries[i]) +
          labs(fill="Style") +
          scale_fill_brewer(palette="Dark2") +
          scale_color_brewer(palette="Dark2") +
          coord_polar(theta="y") +
          xlim(c(-1, 4)) +
          theme_dark() +
          theme(plot.title = element_text(face="bold",family=c("sans"),size=10),
                panel.grid=element_blank(),
                panel.border=element_blank(),
                axis.text = element_blank(),
                axis.ticks = element_blank()
                )
    plist[[i]] <- p
    }
    return(plist)
}

plist <- generate_donuts(data)

wrap_plots(plist) + plot_layout(guides = "collect") & theme(legend.position = "right")


```

# Save Image

Save your image for sharing. Be sure to use the `#TidyTuesday` hashtag in your post on twitter! 

```{r}

# This will save your most recent plot
ggsave(
  filename = "My TidyTuesday Plot.png",
  device = "png", dpi=500)
```
