---
title: "TidyTemplate"
date: 2021-03-04
output: html_output
---

# TidyTuesday


```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(tidytuesdayR)
library(ggplot2)
library(hrbrthemes)
library(lubridate)
library(patchwork)
```

# Load the weekly Data

Download the weekly data and make available in the `tt` object.

```{r Load}

tt <- tt_load("2019-10-08")

```

# Glimpse Data

Take an initial look at the format of the data available.

```{r Glimpse}

tt %>% 
  map(glimpse)

```

# Wrangle

Explore the data and process it into a nice format for plotting! Access each dataset by name by using a dollarsign after the `tt` object and then the name of the data set.

```{r Wrangle}
data <- tt$ipf_lifts

data <- data %>%
  select(c(best3squat_kg,best3bench_kg, best3deadlift_kg, date )) %>%
  filter(best3squat_kg > 0, best3bench_kg > 0, best3deadlift_kg > 0 ) %>%
  mutate(year = year(date),
         month = month(date)) %>%
  group_by(year, month) %>%
  summarize(max_squat=max(best3squat_kg),
            max_bench=max(best3bench_kg),
            max_deadlift=max(best3deadlift_kg))%>%
  pivot_longer(cols = starts_with("max"), names_to = "lift_type", values_to = "weight_kg")%>%
  mutate(day="01",
         date=paste(year, month, day, sep = "-"))%>%
  ungroup()%>%
  select(- c(year, month, day))


```


# Visualize

Using your processed dataset, create your unique visualization.

```{r Visualize}

 ggplot(data, aes(x=as.Date(date), y = weight_kg)) +
  geom_line(aes(color = lift_type)) +
  geom_point() +
  theme_ipsum() +
  labs(title = "Max lifts in time (from 2010 to 2020)",
       x = "Year",
       y = "Weight in Kg",
       color = "Type of lift") +
  theme(axis.text.x=element_text(angle=60, hjust=1)) +
  scale_x_date(limit=c(as.Date("2010-01-01"),as.Date("2020-01-31"))) +
  ylim(150,500)


```

# Save Image

Save your image for sharing. Be sure to use the `#TidyTuesday` hashtag in your post on twitter! 

```{r}

# This will save your most recent plot
ggsave(
  filename = "My TidyTuesday Plot.png",
  device = "png", dpi=500)
```
