---
title: "TidyTemplate"
date: 2021-03-02
output: html_output
---

# TidyTuesday


```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(tidytuesdayR)
library(ggplot2)
library(viridis)
library(hrbrthemes)
```

# Load the weekly Data

Download the weekly data and make available in the `tt` object.

```{r Load}

tt <- tt_load("2019-01-29")

```

# Glimpse Data

Take an initial look at the format of the data available.

```{r Glimpse}

tt %>% 
  map(glimpse)

```

# Wrangle

Explore the data and process it into a nice format for plotting! Access each dataset by name by using a dollarsign after the `tt` object and then the name of the data set.

```{r Wrangle}

data <- tt$state_milk_production


data <- data  %>%
  group_by(year,region) %>%
  summarise(n = sum(milk_produced)) %>%
  mutate(percentage = n / sum(n))


```


# Visualize

Using your processed dataset, create your unique visualization.

```{r Visualize}
ggplot(data, aes(x=year, y=percentage, fill=region)) + 
    geom_area(alpha=0.6 , size=.5, colour="white") +
    scale_fill_viridis(discrete = TRUE, option="A") +
    theme_ipsum() + 
  theme(
    plot.title = element_text( size = 20),
         axis.text.x = element_text(size = 7),
         axis.text.y = element_text(size = 7)) +
    labs(title="Milk production by US regions",
         y="Percentage",
         x="Year",
         fill="Region")

```

# Save Image

Save your image for sharing. Be sure to use the `#TidyTuesday` hashtag in your post on twitter! 

```{r}

# This will save your most recent plot
ggsave(
  filename = "My TidyTuesday Plot.png",
  device = "png", dpi=500)
```
